EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-22 draft.tex
Reformatting and rewriting

On the other hand, there are several caveats as well:
It is more costly to move entire populations as messages than only passing certain individuals 
from a process to another. Designers must consider this cost when working with large
individuals, and if possible send populations using several messages, use compression or 
adjust the size of populations. Pool-based algorithms also suffer from this drawback, but 
web based implementations have been working with continuous optimization problems of 1000 dimensions.
But, in other cases this is not a viable approach.

@@

Finally, the proposed PSO\&GA mixed algorithm has reached the $10^{-8}$ target
value on all functions ($f_1-f_5$) and scales well to higher dimensions, even on
$f_3$ and $f_4$ (charts on the lower rows), which are usually considered
difficult functions. This experiment also exemplifies the type of analyses that
we can perform with the results of the EvoSwarm application by reusing the COCO framework.
We also proved that multi-population algorithms can be compared under the same 
conditions, including single and multi-algorithm versions, and results show 
that the later have better performance.

>>>>

On the other hand, there are several caveats as well: It is more
costly to move entire populations as messages than only passing
certain individuals from a process to another. Designers must consider
this cost when working with large individuals, and if possible send
populations using several messages, use compression or adjust the size
of populations. Pool-based algorithms also suffer from this drawback,
but web based implementations have been working with continuous
optimization problems with 1000 dimensions.  However, in other cases
this is not a viable approach.

@@

Finally, the proposed PSO\&GA hybrid algorithm has reached the $10^{-8}$ target
value on all functions ($f_1-f_5$) and scales well to higher dimensions, even on
$f_3$ and $f_4$ (charts on the lower rows), which are usually considered
difficult functions. This experiment also exemplifies the type of analyses that
we can perform with the results of the EvoSwarm application by reusing the COCO framework.
We also proved that multi-population algorithms can be compared under the same 
conditions, including single and multi-algorithm versions, and results show 
that the later have better performance.
